---
title: "ANOVA"
author: "Elizabeth Telford"
date: "29 January 2019"
output: html_document
---

```{r,echo=FALSE}
library(ggplot2)
library(colorspace)
library(readr)
library(xtable)
library(data.table)
library(car)
library(stargazer)



theme.clean <- function(){
  theme_bw()+
    theme(axis.text.x = element_text(size = 12, angle = 0, vjust = 1, hjust = 1),
          axis.text.y = element_text(size = 12),
          axis.title.x = element_text(size = 12, face = "plain"),             
          axis.title.y = element_text(size = 12, face = "plain"),             
          panel.grid.major.x = element_blank(),                                          
          panel.grid.minor.x = element_blank(),
          panel.grid.minor.y = element_blank(),
          panel.grid.major.y = element_blank(),  
          plot.margin = unit(c(0.5, 0.5, 0.5, 0.5), units = , "cm"),
          plot.title = element_text(size = 20, vjust = 1, hjust = 0.5),
          legend.text = element_text(size = 12, face = "italic"),          
          legend.title = element_blank(),                              
          legend.position = c(0.9, 0.9))
}

stable_iso_area <- read_csv("C:/Users/s1014831/Desktop/Statistics/stable_iso_area.csv")
VS<-subset(stable_iso_area, Species == 'VS')
VE<-subset(stable_iso_area, Species == 'VE')
iso<-stable_iso_area

LabHarvestCSV <- read_csv("C:/Users/s1014831/Desktop/Statistics/LabHarvestCSV.csv")
LabHarvest<-LabHarvestCSV
LabHarvest<-na.omit(LabHarvest)
LabHarvest$Treatment <- factor(LabHarvest$Treatment, levels=c('4%','8%','16%'))
LabHarvest$Species<-factor(LabHarvest$Species, levels=c('VS','VE'))
LabHarvest$Harvest<-as.factor(LabHarvest$Harvest)
LabHarvest$Tag<-as.factor(LabHarvest$Tag)
LabHarvest$Treatment<-as.factor(LabHarvest$Treatment)
LabHarvest_VS<-subset(LabHarvest, Species=="VS")
LabHarvest_VE<-subset(LabHarvest, Species=="VE")

```

#2 way ANOVA for LMA and foliage biochemical traits 

##LMA
```{r,echo=FALSE}
#using an ANOVA for H3 SLA 
hist(VS$SLA)
#left skewed
log_SLA<-log(VS$SLA)
hist(log_SLA)
SLA.aov <- aov(log_SLA ~ Treatment , data = VS)
summary(SLA.aov)
TukeyHSD(SLA.aov)
model.tables(SLA.aov, "means")
plot(SLA.aov, 1)
#3 outliers
leveneTest(log_SLA~ Treatment, data = VS)

# p-value <0.05 no evidence  that the variance across groups is statistically significant
```
##LMA
```{r,echo=FALSE}
#using an ANOVA for H3 SLA 
hist(VE$SLA)
#left skewed
log_SLA<-sqrt(VE$SLA)
hist(log_SLA)
SLA.aov.ve <- aov(log_SLA ~ Treatment , data = VE)
summary(SLA.aov.ve)
TukeyHSD(SLA.aov.ve)
model.tables(SLA.aov.ve, "means")
plot(SLA.aov.ve, 1)
#3 outliers
leveneTest(log_SLA~ Treatment, data = VE)
# p-value <0.05 no evidence  that the variance across groups is statistically significant
```
##15N
```{r,echo=FALSE}
hist(VS$delta15N)
log_15N<-sqrt(VS$delta15N)
hist(log_15N)
N15.aov <- aov(log_15N ~ Treatment , data = VS)
summary(N15.aov)
model.tables(N15.aov, "means")
TukeyHSD(N15.aov)
plot(N15.aov, 1)
#3 outliers
leveneTest(log_15N~ Treatment , data = VS)
# p-value <0.05 no evidence  that the variance across groups is statistically significant
```

##15N
```{r,echo=FALSE}
hist(VE$delta15N)
log_15N<-log10(VE$delta15N)
hist(log_15N)
N15.aov.ve <- aov(log_15N ~ Treatment , data = VE)
summary(N15.aov.ve)
model.tables(N15.aov.ve, "means")
TukeyHSD(N15.aov.ve)
plot(N15.aov.ve, 1)
#3 outliers
leveneTest(log_15N~ Treatment , data = VE)
```


##13C
```{r,echo=FALSE}
hist(VS$delta13C)
log_13C<-sqrt(VE$delta13C)
C13.aov <- aov(delta13C ~ Treatment , data = VS)
summary(C13.aov)
model.tables(C13.aov, "means")
TukeyHSD(C13.aov)
plot(C13.aov, 1)
#3 outliers
leveneTest(delta13C~ Treatment*Species , data = iso)
# p-value <0.05 no evidence  that the variance across groups is statistically significant
```
##13C
```{r,echo=FALSE}
#using an ANOVA for H3 13C
hist(VE$delta13C)
#left skewed
#cannot log as the data is negative 
C13.aov.ve <- aov(delta13C ~ Treatment , data = VE)
summary(C13.aov.ve)
model.tables(C13.aov.ve, "means")
TukeyHSD(C13.aov.ve)
plot(C13.aov.ve, 1)
#3 outliers
leveneTest(delta13C~ Treatment , data = VE)
# p-value <0.05 no evidence  that the variance across groups is statistically significant
```
##N
```{r, echo=FALSE}
#using an ANOVA for H3 N
hist(VS$N)
log_N<-log10(VS$N)
hist(log_N)
N.aov <- aov(log_N ~ Treatment , data = VS)
summary(N.aov)
model.tables(N.aov, "means")
TukeyHSD(N.aov)
plot(N.aov, 1)
#3 outliers
leveneTest(N~ Treatment , data = VS)
# p-value <0.05 no evidence  that the variance across groups is statistically significant
```
##N
```{r, echo=FALSE}
hist(VE$N)
log_N<-log(VE$N)
hist(log_N)
N.aov.ve <- aov(N ~ Treatment , data = VE)
summary(N.aov.ve)
model.tables(N.aov.ve, "means")
TukeyHSD(N.aov.ve)
plot(N.aov.ve, 1)
#3 outliers
leveneTest(N~ Treatment , data = VE)
# p-value <0.05 no evidence  that the variance across groups is statistically significant
```
##c
```{r, echo=FALSE}
#using an ANOVA for H3 C
hist(VS$C)
#left skewed
log_C<-sqrt(VS$C)
hist(log_C)
#cannot log as the data is negative 
C.aov <- aov(C ~ Treatment , data = VS)
summary(C.aov)
model.tables(C.aov, "means")
TukeyHSD(C.aov)
plot(C.aov, 1)
#3 outliers
leveneTest(C~ Treatment , data = VS)
# p-value <0.05 no evidence  that the variance across groups is statistically significant
```

##C
```{r, echo=FALSE}
#using an ANOVA for H3 C
hist(VE$C)
#left skewed
log_C<-log10(VE$C)
hist(log_C)
#cannot log as the data is negative 
C.aov.ve <- aov(C ~ Treatment , data = VE)
summary(C.aov.ve)
model.tables(C.aov.ve, "means")
TukeyHSD(C.aov.ve)
plot(C.aov.ve, 1)
#3 outliers
leveneTest(C~ Treatment , data = VE)
# p-value <0.05 no evidence  that the variance across groups is statistically significant
```

##C:N
```{r,echo=FALSE}
#using an ANOVA for H3 C:N ratio
hist(VS$CN_ratio)
#left skewed
log_CN<-sqrt(VS$CN_ratio)
hist(log_CN)
CN.aov <- aov(log_CN ~ Treatment , data = VS)
summary(CN.aov)
model.tables(CN.aov, "means")
TukeyHSD(CN.aov)
plot(CN.aov, 1)
#3 outliers
leveneTest(log_CN~ Treatment , data = VS)
# p-value <0.05 no evidence  that the variance across groups is statistically significant
```

##C:N
```{r,echo=FALSE}
#using an ANOVA for H3 C:N ratio
hist(VE$CN_ratio)
#left skewed
log_CN<-sqrt(VE$CN_ratio)
hist(log_CN)
#cannot log as the data is negative 
CN.aov.ve <- aov(log_CN ~ Treatment , data = VE)
summary(CN.aov.ve)
model.tables(CN.aov.ve, "means")
TukeyHSD(CN.aov.ve)
plot(CN.aov.ve, 1)
#3 outliers
leveneTest(log_CN~ Treatment , data = VE)
# p-value <0.05 no evidence  that the variance across groups is statistically significant
```

#Table of results

__V.sieberiana Leaf Mass per Area (LMA)__
```{r, results='asis',echo=FALSE}
library(xtable)
t1<-print(xtable(SLA.aov), type="html" )
```
__V.sieberiana Leaf 15N__
```{r, results='asis',echo=FALSE}
t2<-print(xtable(N15.aov), type = "html", head ="Leaf 15N")
```
__V.sieberiana Leaf 13C__
```{r, results='asis',echo=FALSE}
t3<-print(xtable(C13.aov), type = "html",head = "Leaf 13C")
```
__V.sieberiana Leaf N__
```{r, results='asis',echo=FALSE}
t4<-print(xtable(N.aov), type = "html", head= "Leaf N")
```
__V.sieberiana Leaf C__
```{r, results='asis',echo=FALSE}
t5<-print(xtable(C.aov), type = "html", head= "Leaf C")
```
__V.sieberiana Leaf C:N__
```{r, results='asis',echo=FALSE}
t6<-print(xtable(CN.aov), type = "html", head= "Leaf C:N")
```


###split


__V.erioloba Leaf Mass per Area (LMA)__
```{r, results='asis',echo=FALSE}
library(xtable)
t1<-print(xtable(SLA.aov.ve), type="html" )
```
__V.erioloba Leaf 15N__
```{r, results='asis',echo=FALSE}
t2<-print(xtable(N15.aov.ve), type = "html", head ="Leaf 15N")
```
__V.erioloba Leaf 13C__
```{r, results='asis',echo=FALSE}
t3<-print(xtable(C13.aov.ve), type = "html",head = "Leaf 13C")
```
__V.erioloba Leaf N__
```{r, results='asis',echo=FALSE}
t4<-print(xtable(N.aov.ve), type = "html", head= "Leaf N")
```
__V.erioloba Leaf C__
```{r, results='asis',echo=FALSE}
t5<-print(xtable(C.aov.ve), type = "html", head= "Leaf C")
```
__V.erioloba Leaf C:N__
```{r, results='asis',echo=FALSE}
t6<-print(xtable(CN.aov.ve), type = "html", head= "Leaf C:N")
```

```{r,echo=FALSE}
#using an ANOVA for H3 C:N ratio
hist(iso$CN_ratio)
#left skewed
log_CN<-log10(iso$CN_ratio)
hist(log_CN)
#cannot log as the data is negative 
CN.aov.ve <- aov(log_CN ~ Treatment+ Species , data = iso)
summary(CN.aov.ve)
model.tables(CN.aov.ve, "means")
TukeyHSD(CN.aov.ve)
plot(CN.aov.ve, 1)
#3 outliers
leveneTest(log_CN~ Treatment*Species , data = iso)
# p-value <0.05 no evidence  that the variance across groups is statistically significant
```
```{r,echo=FALSE}
#using an ANOVA for H3 C:N ratio
#left skewed
log_CN<-log10(iso$CN_ratio)
hist(log_CN)
#cannot log as the data is negative 
CN.aov.ve <- aov(log_CN ~ Treatment+ Species , data = iso)
summary(CN.aov.ve)
model.tables(CN.aov.ve, "means")
TukeyHSD(CN.aov.ve)
plot(CN.aov.ve, 1)
#3 outliers
leveneTest(log_CN~ Treatment*Species , data = iso)
# p-value <0.05 no evidence  that the variance across groups is statistically significant
```

```{r,echo=FALSE}
#using an ANOVA for H3 13C
hist(iso$delta13C)
C13.aov.ve <- aov(delta13C ~ Treatment + Species , data = iso)
summary(C13.aov.ve)
model.tables(C13.aov.ve, "means")
TukeyHSD(C13.aov.ve)
plot(C13.aov.ve, 1)
#3 outliers
leveneTest(delta13C~ Treatment*Species , data = iso)
# p-value <0.05 no evidence  that the variance across groups is statistically significant
```
```{r,echo=FALSE}
#using an ANOVA for H3 13C
hist(iso$N)
N.aov.ve <- aov(N ~ Treatment + Species , data = iso)
summary(N.aov.ve)
model.tables(N.aov.ve, "means")
TukeyHSD(N.aov.ve)
plot(N.aov.ve, 1)
#3 outliers
leveneTest(N~ Treatment*Species , data = iso)
# p-value <0.05 no evidence  that the variance across groups is statistically significant
```


###13c and c:N 

__Leaf 13C__
```{r, results='asis',echo=FALSE}
t6<-print(xtable(C13.aov.ve), type = "html", head= "Nodule Count")
```
__Leaf C:N ratio__
```{r, results='asis',echo=FALSE}
t6<-print(xtable(CN.aov.ve), type = "html", head= "Nodule Weight (grams)")
```
__Leaf N__
```{r, results='asis',echo=FALSE}
t6<-print(xtable(N.aov.ve), type = "html", head= "Nodule Weight (grams)")
```



##growth

```{r, echo=FALSE}
LabHarvestCSV <- read_csv("C:/Users/s1014831/Desktop/LabHarvestCSV.csv")

LabHarvest<-LabHarvestCSV
#using an ANOVA for H3 SLA 
hist(LabHarvest$Height)
#left skewed
log_TDW<-sqrt(LabHarvest$Height)
hist(log_TDW)
TDW.aov <- aov(log_TDW ~ Treatment*Species*Harvest , data = LabHarvest)
summary(TDW.aov)
TukeyHSD(TDW.aov)
model.tables(TDW.aov, "means")
plot(TDW.aov, 1)
#3 outliers
leveneTest(log_TDW~ Treatment*Species*Harvest, data = LabHarvest)
# p-value <0.05 no evidence  that the variance across groups is statistically significant
```

##Below ground 
```{r, echo=FALSE}
LabHarvestCSV <- read_csv("C:/Users/s1014831/Desktop/LabHarvestCSV.csv")

LabHarvest<-LabHarvestCSV
H3<- subset(LabHarvest, Harvest=="H3")
hist(H3$BG_DW)
#left skewed
log_BGW<-log10(H3$BG_DW)
hist(log_BGW)

BGW.aov <- aov(log_BGW ~ Treatment + Species , data = H3)
summary(BGW.aov)
TukeyHSD(BGW.aov)
model.tables(BGW.aov, "means")
plot(BGW.aov, 1)
#3 outliers
leveneTest(log_BGW ~ Treatment * Species, data = H3)
# p-value <0.05 no evidence  that the variance across groups is statistically significant
```
##Below ground 
```{r, echo=FALSE}
hist(H3$R_S)
#left skewed
log_AGW<-log2(H3$R_S)
hist(log_AGW)
AGW.aov <- aov(log_AGW ~ Treatment + Species , data = H3)
summary(AGW.aov)
TukeyHSD(AGW.aov)
model.tables(AGW.aov, "means")
plot(AGW.aov, 1)
#3 outliers
leveneTest(log_AGW ~ Treatment * Species, data = H3)
# p-value <0.05 no evidence  that the variance across groups is statistically significant
```
```{r,echo=FALSE}
#using an ANOVA for H3 SLA 
hist(iso$SLA)
#left skewed
log_SLA<-sqrt(iso$SLA)
hist(log_SLA)
SLA.aov.ve <- aov(log_SLA ~ Treatment + Species , data = iso)
summary(SLA.aov.ve)
TukeyHSD(SLA.aov.ve)
model.tables(SLA.aov.ve, "means")
plot(SLA.aov.ve, 1)
#3 outliers
leveneTest(log_SLA~ Treatment* Species, data = iso)
# p-value <0.05 no evidence  that the variance across groups is statistically significant
```
__Belowground dry weight (grams)__
```{r, results='asis',echo=FALSE}
t6<-print(xtable(AGW.aov), type = "html", head= "Plant Weight (g)")
```
__Root: Shoot ratio__
```{r, results='asis',echo=FALSE}
t6<-print(xtable(BGW.aov), type = "html", head= "V.sieberiana Belowground dry weight (grams)")
```
__Leaf Mass per Area__
```{r, results='asis',echo=FALSE}
t6<-print(xtable(SLA.aov.ve), type = "html", head= "V.sieberiana Belowground dry weight (grams)")
```

##break


__Nodule Count__
```{r,results='asis',echo=FALSE}
hist(LabHarvest_VS$Nodule)
#left skewed
log_N<-sqrt(LabHarvest_VS$Nodule)
hist(log_N)
N.aov <- aov(log_N~ Treatment + Harvest , data = LabHarvest_VS)
summary(N.aov)
TukeyHSD(N.aov)
model.tables(N.aov, "means")
plot(N.aov, 1)
#3 outliers
leveneTest(Nodule~ Treatment*Harvest, data = LabHarvest_VS)
# p-value <0.05 no evidence  that the variance across groups is statistically significant
```
__Nodule Weight__
```{r,results='asis',echo=FALSE}
hist(LabHarvest_VS$Nodules_W)
#left skewed
log_N<-log(LabHarvest_VS$Nodules_W)
hist(log_N)
Nw.aov <- aov(log_N~ Treatment + Harvest , data = LabHarvest_VS)
summary(Nw.aov)
TukeyHSD(Nw.aov)
model.tables(Nw.aov, "means")
plot(Nw.aov, 1)
#3 outliers
leveneTest(Nodules_W~ Treatment*Harvest, data = LabHarvest_VS)
```
__Biological Nitrogen Fixation__
```{r,results='asis',echo=FALSE}
SI_VS<-subset(iso, Species=="VS")
#using an ANOVA for H3 BNF
hist(SI_VS$Nf)
#left skewed
log_Nf<-sqrt(SI_VS$Nf)
hist(log_Nf)
BNF.aov <- aov(log_Nf ~ Treatment , data = SI_VS)
summary(BNF.aov)
TukeyHSD(BNF.aov)
model.tables(BNF.aov, "means")
plot(BNF.aov, 1)
#3 outliers
leveneTest(log_Nf~ Treatment, data = SI_VS)
# p-value <0.05 no evidence  that the variance across groups is statistically significant
```

__Biological Nitrogen Fixation__
```{r,results='asis',echo=FALSE}
SI_VS<-subset(iso, Species=="VS")
#using an ANOVA for H3 BNF
hist(iso$delta15N)
#left skewed
log_Nf<-log10(iso$delta15N)
hist(log_Nf)
N15.aov <- aov(log_Nf ~ Treatment+ Species , data = iso)
summary(N15.aov)
TukeyHSD(N15.aov)
model.tables(N15.aov, "means")
plot(N15.aov, 1)
#3 outliers
leveneTest(log_Nf~ Treatment*Species, data = iso)
# p-value <0.05 no evidence  that the variance across groups is statistically significant
```

__Nodule Count__
```{r, results='asis',echo=FALSE}
t6<-print(xtable(N.aov), type = "html", head= "Nodule Count")
```
__Nodule Weight (grams)__
```{r, results='asis',echo=FALSE}
t6<-print(xtable(Nw.aov), type = "html", head= "Nodule Weight (grams)")
```
__Leaf 15N__
```{r, results='asis',echo=FALSE}
t6<-print(xtable(N15.aov), type = "html", head= "Biological Nitrogen fixation")
```
__Biological Nitrogen Fixation__
```{r, results='asis',echo=FALSE}
t6<-print(xtable(BNF.aov), type = "html", head= "Biological Nitrogen fixation")
```



##break


```{r, results='asis'}
stargazer(N.aov, type = "html",
          digits = 3,
          star.cutoffs = c(0.05, 0.01, 0.001),
          digit.separator = "")
```

__Looking at the LICOR data__
```{r,echo=FALSE}
LICOR <- read_csv("C:/Users/s1014831/Desktop/Statistics/LICOR.csv")
LICOR$Treatment <- factor(LICOR$Treatment, levels=c('4%','8%','16%'))
LICOR$Species <- factor(LICOR$Species, levels=c('VS','VE'))
LICOR<-na.omit(LICOR)
VS<-subset(LICOR, Species == 'VS')
VE<-subset(LICOR, Species == 'VE')
```
__LSA (mm2) VS__
```{r,results='asis',echo=FALSE}
hist(VS$Leaf_Area)
log_LSA<-log10(VS$Leaf_Area)
hist(log_LSA)
LSA.aov <- aov(log_LSA ~ Treatment + Harvest , data = VS)
summary(LSA.aov)
TukeyHSD(LSA.aov)
model.tables(LSA.aov, "means")
plot(LSA.aov, 1)
#3 outliers
leveneTest(log_LSA~ Treatment*Harvest, data = VS)
# p-value <0.05 no evidence  that the variance across groups is statistically significant
```
__LSA (mm2) VE__
```{r,results='asis',echo=FALSE}
hist(VE$Leaf_Area)
log_LSA<-log10(VE$Leaf_Area)
hist(log_LSA)
LSA.aov.ve <- aov(log_LSA ~ Treatment + Harvest , data = VE)
summary(LSA.aov.ve)
TukeyHSD(LSA.aov)
model.tables(LSA.aov.ve, "means")
plot(LSA.aov.ve, 1)
#3 outliers
leveneTest(log_LSA~ Treatment*Harvest, data = VE)
# p-value <0.05 no evidence  that the variance across groups is statistically significant
```
__Ci (umol mol) VS__
```{r,results='asis',echo=FALSE}
hist(VS$Ci_Ca)
log_Ci<-log2(VS$Ci_Ca)
hist(log_Ci)
Ci.aov <- aov(log_Ci ~ Treatment + Harvest , data = VS)
summary(Ci.aov)
TukeyHSD(Ci.aov)
model.tables(Ci.aov, "means")
plot(Ci.aov, 1)
#3 outliers
leveneTest(log_Ci~ Treatment * Harvest, data = VS)
# p-value <0.05 no evidence  that the variance across groups is statistically significant
```

__Ci (umol mol) VE__
```{r,results='asis',echo=FALSE}
hist(VE$Ci_Ca)
#left skewed
log_Ci<-sqrt(VE$Ci_Ca)
hist(log_Ci)
Ci.aov.ve <- aov(log_Ci ~ Treatment + Harvest , data = VE)
summary(Ci.aov.ve)
TukeyHSD(Ci.aov.ve)
model.tables(Ci.aov.ve, "means")
plot(Ci.aov.ve, 1)
#3 outliers
leveneTest(log_Ci~ Treatment*Harvest, data = VE)
# p-value <0.05 no evidence  that the variance across groups is statistically significant
```
__Amax (umol m-2 s-1) VS__
```{r,results='asis',echo=FALSE}
hist(VS$Amax)
#left skewed
log_Amax<-log2(VS$Amax)
hist(log_Amax)
Amax.aov <- aov(log_Amax ~ Treatment + Harvest , data = VS)
summary(Amax.aov)
TukeyHSD(Amax.aov)
model.tables(Amax.aov, "means")
plot(Amax.aov, 1)
#3 outliers
leveneTest(log_Amax~ Treatment*Harvest*Species, data = VS)
# p-value <0.05 no evidence  that the variance across groups is statistically significant
```
__Amax (umol m-2 s-1) VE__
```{r,results='asis',echo=FALSE}
hist(VE$Amax)
#left skewed
log_Amax<-log(VE$Amax)
hist(log_Amax)
Amax.aov.ve <- aov(log_Amax ~ Treatment + Harvest , data = VE)
summary(Amax.aov.ve)
TukeyHSD(Amax.aov.ve)
model.tables(Amax.aov.ve, "means")
plot(Amax.aov.ve, 1)
#3 outliers
leveneTest(log_Amax~ Treatment*Harvest*Species, data = VE)
# p-value <0.05 no evidence  that the variance across groups is statistically significant
```
__V.sieberiana LSA (mm2)__
```{r, results='asis',echo=FALSE}
t6<-print(xtable(LSA.aov), type = "html", head= "V.sieberiana LSA (mm2)")
```
__V.sieberiana Ci:Ca__
```{r, results='asis',echo=FALSE}
t6<-print(xtable(Ci.aov), type = "html", head= "V.sieberiana Ci (umol mol)")
```
__V.sieberiana Amax (umol m-2 s-1)__
```{r, results='asis',echo=FALSE}
t6<-print(xtable(Amax.aov), type = "html", head= "V.sieberiana Amax (umol m-2 s-1)")
```
__V.erioloba LSA (mm2)__
```{r, results='asis',echo=FALSE}
t6<-print(xtable(LSA.aov.ve), type = "html", head= "V.erioloba LSA (mm2)")
```
__V.erioloba Ci:Ca__
```{r, results='asis',echo=FALSE}
t6<-print(xtable(Ci.aov.ve), type = "html", head= "V.erioloba Ci (umol mol)")
```

__V.erioloba Amax (umol m-2 s-1)__
```{r, results='asis',echo=FALSE}
t6<-print(xtable(Amax.aov.ve), type = "html", head= "V.sieberiana Amax (umol m-2 s-1)")
```


__LSA (mm2) VS__
```{r,results='asis',echo=FALSE}
L3<-subset(LICOR, Harvest =="H3")
hist(L3$Leaf_Area)
log_LSA<-log10(L3$Leaf_Area)
hist(log_LSA)
LSA.aov <- aov(log_LSA ~ Treatment + Species , data = L3)
summary(LSA.aov)
TukeyHSD(LSA.aov)
model.tables(LSA.aov, "means")
plot(LSA.aov, 1)
#3 outliers
leveneTest(log_LSA~ Treatment*Species, data = L3)
# p-value <0.05 no evidence  that the variance across groups is statistically significant
```

__Ci (umol mol) VE__
```{r,results='asis',echo=FALSE}
hist(L3$Ci_Ca)
#left skewed
log_Ci<-sqrt(L3$Ci_Ca)
hist(log_Ci)
Ci.aov.ve <- aov(log_Ci ~ Treatment + Species , data = L3)
summary(Ci.aov.ve)
TukeyHSD(Ci.aov.ve)
model.tables(Ci.aov.ve, "means")
plot(Ci.aov.ve, 1)
#3 outliers
leveneTest(log_Ci~ Treatment*Species, data = L3)
# p-value <0.05 no evidence  that the variance across groups is statistically significant
```
__Amax (umol m-2 s-1) VS__
```{r,results='asis',echo=FALSE}
hist(L3$Amax)
#left skewed
log_Amax<-log2(L3$Amax)
hist(log_Amax)
Amax.aov <- aov(log_Amax ~ Treatment + Species , data = L3)
summary(Amax.aov)
TukeyHSD(Amax.aov)
model.tables(Amax.aov, "means")
plot(Amax.aov, 1)
#3 outliers
leveneTest(log_Amax~ Treatment*Species, data = L3)
# p-value <0.05 no evidence  that the variance across groups is statistically significant
```
__LSA (mm2)__
```{r, results='asis',echo=FALSE}
t6<-print(xtable(LSA.aov), type = "html", head= "V.erioloba LSA (mm2)")
```
__Ci:Ca__
```{r, results='asis',echo=FALSE}
t6<-print(xtable(Ci.aov.ve), type = "html", head= "V.erioloba Ci (umol mol)")
```

__Amax (umol m-2 s-1)__
```{r, results='asis',echo=FALSE}
t6<-print(xtable(Amax.aov), type = "html", head= "V.sieberiana Amax (umol m-2 s-1)")
```




##end