---
title: "H3 Basic models"
author: "Elizabeth"
date: "7 November 2018"
output: html_document
---

```{r}
library(readxl)
LabHarveste <- read_excel("C:/Users/telfo/Desktop/LabHarveste.xlsx")
View(LabHarveste)
LabHarvest<-LabHarveste
library(ggplot2)
library(agridat)
```


```{r}
#setting factors
LabHarvest$Treatment <- as.factor(LabHarvest$Treatment)
LabHarvest$Harvest<-as.factor(LabHarvest$Harvest)
LabHarvest$Tag<-as.factor(LabHarvest$Tag)
```


```{r}
#subsetting data
LabHarvest_H1 <- subset(LabHarvest,Harvest=="1")
LabHarvest_H1_VS <- subset(LabHarvest_H1,Species=="VS")
LabHarvest_H1 <- subset(LabHarvest,Harvest=="1")
LabHarvest_H1_VE <- subset(LabHarvest_H1,Species=="VE")
LabHarvest_H2 <- subset(LabHarvest,Harvest=="2")
LabHarvest_H2_VS <- subset(LabHarvest_H2,Species=="VS")
LabHarvest_H2 <- subset(LabHarvest,Harvest=="2")
LabHarvest_H2_VE <- subset(LabHarvest_H2,Species=="VE")
LabHarvest_H3 <- subset(LabHarvest,Harvest=="3")
LabHarvest_H3_VS <- subset(LabHarvest_H3,Species=="VS")
LabHarvest_H3 <- subset(LabHarvest,Harvest=="3")
LabHarvest_H3_VE <- subset(LabHarvest_H3,Species=="VE")

LabHarvest_VS<-subset(LabHarvest, Species=="VS")
LabHarvest_VE<-subset(LabHarvest, Species=="VE")
```

```{r}
theme.clean <- function(){
  theme_bw()+
    theme(axis.text.x = element_text(size = 12, angle = 45, vjust = 1, hjust = 1),
          axis.text.y = element_text(size = 12),
          axis.title.x = element_text(size = 14, face = "plain"),             
          axis.title.y = element_text(size = 14, face = "plain"),             
          panel.grid.major.x = element_blank(),                                          
          panel.grid.minor.x = element_blank(),
          panel.grid.minor.y = element_blank(),
          panel.grid.major.y = element_blank(),  
          plot.margin = unit(c(0.5, 0.5, 0.5, 0.5), units = , "cm"),
          plot.title = element_text(size = 20, vjust = 1, hjust = 0.5),
          legend.text = element_text(size = 12, face = "italic"),          
          legend.title = element_blank(),                              
          legend.position = c(0.9, 0.9))
}
```

#Total weight vs Treatment + Species 
```{r}
(LabHarvest_H3_TDW.p <- ggplot(LabHarvest_H2, aes(Tag, Total_DW)) + geom_boxplot(fill = "#CD3333", alpha = 0.8, colour = "#8B2323") + theme.clean() +  theme(axis.text.x = element_text(size = 12, angle = 0)) + labs(x = "Species & Treatment (%)", y = "Total Dry weight (grams)"))

#linear model grouping species not signifciant 

LabHarvest_H3_VS_TDW.m<-lm(Total_DW~Treatment, data= LabHarvest_H3_VS)
summary(LabHarvest_H3_VS_TDW.m)

LabHarvest_H3_VE_TDW.m<-lm(Total_DW~Treatment, data= LabHarvest_H3_VE)
summary(LabHarvest_H3_VE_TDW.m)

#not significant at all 

```

#Belowground weight vs Treatment + Species
```{r}
(LabHarvest_H3_BGDW.p <- ggplot(LabHarvest_H3, aes(Tag, BG_DW)) + geom_boxplot(fill = "#CD3333", alpha = 0.8, colour = "#8B2323") + theme.clean() +  theme(axis.text.x = element_text(size = 12, angle = 0)) + labs(x = "Species & Treatment (%)", y = " Below Ground Dry Weight (grams)"))

LabHarvest_H3_BGDW.m<-lm(BG_DW~Treatment + Species, data= LabHarvest_H3)
summary(LabHarvest_H3_BGDW.m)

#not signifant lm value when species are grouped or VS or VE
#doesnt seem to effected by species

```

#Aboveground weight vs Treatment + Species
```{r}
(H3_AGDW.p <- ggplot(LabHarvest_H3, aes(Tag, AG_DW)) 
    +  geom_boxplot(fill = "#CD3333", alpha = 0.8, colour = "#8B2323") 
    +  theme.clean()   
    + theme(axis.text.x = element_text(size = 12, angle = 0)) + labs(x = "Species & Treatment (%)", y = "Aboveground Dry Weight (grams)"))
    
LabHarvest_H3_AGDW.m<-lm(AG_DW~Treatment + Species, data= LabHarvest_H3)
summary(LabHarvest_H3_AGDW.m)

H3_AGDW.resid<-resid(LabHarvest_H3_AGDW.m)
shapiro.test(H3_AGDW.resid)

bartlett.test(LabHarvest_H3$AG_DW,LabHarvest_H3$Treatment)

```

#Leaf weight vs Treatment + Species
```{r}
(LabHarvest_H3_leaf.p <- ggplot(LabHarvest_H3, aes(Tag, Leaves_DW)) + geom_boxplot(fill = "#CD3333", alpha = 0.8, colour = "#8B2323") + theme.clean() +  theme(axis.text.x = element_text(size = 12, angle = 0)) + labs(x = "Species & Treatment (%)", y = "Leaf Dry weight (grams)"))

LabHarvest_H3_leafDW.m<-lm(Leaves_DW~Treatment + Species , data= LabHarvest_H3)
summary(LabHarvest_H3_leafDW.m)

H3_leafDW.resid<-resid(LabHarvest_H3_leafDW.m)
shapiro.test(H3_leafDW.resid)

bartlett.test(LabHarvest_H3$Leaves_DW,LabHarvest_H3$Treatment)

```

#Height vs Treatment + Species
```{r}
(LabHarvest_H3_Height.p <- ggplot(LabHarvest_H3, aes(Tag, Height)) + geom_boxplot(fill = "#CD3333", alpha = 0.8, colour = "#8B2323") + theme.clean() +  theme(axis.text.x = element_text(size = 12, angle = 0)) + labs(x = "Species & Treatment (%)", y = "Height (mm)"))

LabHarvest_H3_Height.m<-lm(Height~Treatment + Species , data= LabHarvest_H3)
summary(LabHarvest_H3_Height.m)

#grouped together doesnt have a significant p value or per species or disreguarding treatment 

```

#Stem vs Treatment + Species
```{r}
(LabHarvest_H3_stalk.p <- ggplot(LabHarvest_H3, aes(Tag, Stem_DW)) + geom_boxplot(fill = "#CD3333", alpha = 0.8, colour = "#8B2323") + theme.clean() +  theme(axis.text.x = element_text(size = 12, angle = 0)) + labs(x = "Species & Treatment (%)", y = "Stem Dry Weight (grams)"))

#model including treatment and species as factors was not significant 

LabHarvest_H3_VS_stalk.m<-lm(Stem_DW~Treatment, data= LabHarvest_H3_VS)
summary(LabHarvest_H3_VS_stalk.m)

LabHarvest_H3_VE_stalk.m<-lm(Stem_DW~Treatment, data= LabHarvest_H3_VE)
summary(LabHarvest_H3_VE_stalk.m)
```

#Examing the effects of Nodules on V.Sieb

#Nodule presence
```{r}
 LabHarvest_H3_Nodule.m <-glm(Nodules_Present~Treatment, family= binomial, data=LabHarvest_H3)
summary(LabHarvest_H3_Nodule.m)
```

#Nodule Count
```{r}
(LabHarvest_H3_Nodules.p <- ggplot(LabHarvest_H3_VS, aes(Tag, Nodule)) + geom_boxplot(fill = "#CD3333", alpha = 0.8, colour = "#8B2323") + theme.clean() +  theme(axis.text.x = element_text(size = 12, angle = 0)) + labs(x = "Species & Treatment (%)", y = "Nodule Count"))

LabHarvest_H3_VS_NOD.m<-lm(Nodule~Treatment, data= LabHarvest_H3_VS)
summary(LabHarvest_H3_VS_NOD.m)
```

#Nodule Weight
```{r}
(LabHarvest_H3_NodulesW.p <- ggplot(LabHarvest_H3_VS, aes(Tag, Nodules_W)) + geom_boxplot(fill = "#CD3333", alpha = 0.8, colour = "#8B2323") + theme.clean() +  theme(axis.text.x = element_text(size = 12, angle = 0)) + labs(x = "Species & Treatment (%)", y = "Nodule Weight (grams)"))

LabHarvest_H3_VS_NODW.m<-lm(Nodules_W~Treatment, data= LabHarvest_H3_VS)
summary(LabHarvest_H3_VS_NODW.m)
```

#Nodule count as a factor 

#Nodule count vs Total weight?
```{r}

LabHarvest_H3_VS_NOD_TDW.m<-lm(Total_DW~Treatment+Nodule, data= LabHarvest_H3_VS)
summary(LabHarvest_H3_VS_NOD_TDW.m)
```

#Nodule count vs Aboveground weight 
```{r}
LabHarvest_H3_VS_NOD_ADW.m<-lm(AG_DW~Treatment+Nodule, data= LabHarvest_H3_VS)
summary(LabHarvest_H3_VS_NOD_ADW.m)
```

#Nodule count vs Belowground weight
```{r}
LabHarvest_H3_VS_NOD_Root.m<-lm(BG_DW~Treatment+Nodule, data= LabHarvest_H3_VS)
summary(LabHarvest_H3_VS_NOD_Root.m)
```

#Nodule count vs Height 
```{r}

LabHarvest_H3_VS_NOD_H.m<-lm(Height~Treatment+Nodule, data= LabHarvest_H3_VS)
summary(LabHarvest_H3_VS_NOD_H.m)
```

#Nodule count vs Leaf weight
```{r}
LabHarvest_H3_NOD_leaf.m<-lm(Leaves_DW~Treatment + Species + Nodule, data= LabHarvest_H3)
summary(LabHarvest_H3_NOD_leaf.m)

LabHarvest_H3_VS_NOD_leaf.m<-lm(Leaves_DW~Treatment + Nodule, data= LabHarvest_H3_VS)
summary(LabHarvest_H3_VS_NOD_leaf.m)
```

#Nodule weight vs Stem weight 
```{r}
LabHarvest_H3_VS_NOD_stem.m<-lm(Stem_DW~Treatment+Nodule, data= LabHarvest_H3_VS)
summary(LabHarvest_H3_VS_NOD_stem.m)

#not significant 
```

#Nodule weight as a factor

#Nodule weight vs Total weight 
```{r}
LabHarvest_H3_VS_NODW_TDW.m<-lm(Total_DW~Treatment+Nodules_W, data= LabHarvest_H3_VS)
summary(LabHarvest_H3_VS_NODW_TDW.m)
```

#Nodule weight vs Aboveground weight 
```{r}
LabHarvest_H3_VS_NODW_ADW.m<-lm(AG_DW~Treatment+Nodules_W, data= LabHarvest_H3_VS)
summary(LabHarvest_H3_VS_NODW_ADW.m)
```

#Nodule weight vs Height 
```{r}
LabHarvest_H3_VS_NODW_H.m<-lm(Height~Treatment+Nodules_W, data= LabHarvest_H3_VS)
summary(LabHarvest_H3_VS_NODW_H.m)
```

#Nodule weight vs Belowground weight
```{r}
LabHarvest_H3_VS_NODW_Root.m<-lm(BG_DW~Treatment+Nodules_W, data= LabHarvest_H3_VS)
summary(LabHarvest_H3_VS_NODW_Root.m)
```

#Nodule weight vs Leaf weight
```{r}
LabHarvest_H3_NODW_leaf.m<-lm(Leaves_DW~Treatment + Species + Nodules_W, data= LabHarvest_H3)
summary(LabHarvest_H3_NODW_leaf.m)

LabHarvest_H3_VS_NODW_leaf.m<-lm(Leaves_DW~Treatment + Nodules_W, data= LabHarvest_H3_VS)
summary(LabHarvest_H3_VS_NODW_leaf.m)

```

#Nodule weight vs Stem weight 
```{r}
LabHarvest_H3_VS_NODW_stem.m<-lm(Stem_DW~Treatment+Nodules_W, data= LabHarvest_H3_VS)
summary(LabHarvest_H3_VS_NODW_stem.m)

#not significant
```